Phenotypic evolution is more constrained in simpler food webs

### 2019-01-11 manuscript.Rmd
added Start, Weis, and Gilbert In Press and removed old beginning to intro.

<!--Summary-->
<!-- Our key finding was that phenotypic evolution in gall midges was more constrained in simpler food webs. More traits contributed to the slope of the adaptive landscape in the simpler food web, suggesting that the trajectory of phenotypic evolution is more constrained. -->
We found that simpler food webs constrained phenotypic evolution in gall midges in two key ways. First, more traits contributed to the slope of the adaptive landscape in the simpler food web, suggesting greater constraints on the trajectory of phenotypic evolution. Second, the simple food-web treatment indirectly increased the number of genetic constraints, which could act to constrain the gall midge's adaptive potential in the face of novel selection pressures. We also found evidence of indirect selection pressures in more complex food webs, suggesting that the adaptive landscape may be more dynamic in complex food webs. Taken together, our study provides experimental evidence from the field that the simplification of ecological communities may constrain the adaptive potential of remaining populations.

@@

<!--Indirect evolutionary effects-->
Our results suggest that the simplification of ecological communities may not only directly affect connected species, but also result in indirect evolutionary effects. In our study, this indirect effect arises from egg parasitoids being released from intraguild predation in simpler food webs. This release occurs more on trees with high larval densities, which could intensify selection on gall midge oviposition preference. A growing number of experiments over the past two decades have demonstrated the presence and potential importance of indirect evolutionary effects that emerge in a community context [@Juenger1998; @Stinchcombe2001; @Lankau2007; @Walsh2008; @Walsh2010; @terHorst2010; @Sahli2011; @Lau2012; @terHorst2015; @Schiestl2018]<!--; Start et al. in press-->. If indirect evolutionary effects are common [@Walsh2013], then predicting evolutionary trajectories resulting from the simplification of food webs will require evolutionary studies to explicitly account for the ecological networks that species are embedded in.

>>>>

<!--Summary-->
We found that simpler food webs constrained phenotypic evolution in gall midges in two key ways. First, more traits contributed to the slope of the adaptive landscape in the simpler food web, suggesting greater constraints on the trajectory of phenotypic evolution. Second, the simple food-web treatment indirectly increased the number of genetic constraints, which could act to constrain the gall midge's adaptive potential in the face of novel selection pressures. We also found evidence of indirect selection pressures in more complex food webs, suggesting that the adaptive landscape may be more dynamic in complex food webs. Taken together, our study provides experimental evidence from the field that the simplification of ecological communities may constrain the adaptive potential of remaining populations.

@@

<!--Indirect evolutionary effects-->
Our results suggest that the simplification of ecological communities may not only directly affect connected species, but also result in indirect evolutionary effects. In our study, this indirect effect arises from egg parasitoids being released from intraguild predation in simpler food webs. This release occurs more on trees with high larval densities, which could intensify selection on gall midge oviposition preference. A growing number of experiments over the past two decades have demonstrated the presence and potential importance of indirect evolutionary effects that emerge in a community context [@Juenger1998; @Stinchcombe2001; @Lankau2007; @Walsh2008; @Walsh2010; @terHorst2010; @Sahli2011; @Lau2012; @terHorst2015; @Schiestl2018; @StartInPress]. If indirect evolutionary effects are common [@Walsh2013], then predicting evolutionary trajectories resulting from the simplification of food webs will require evolutionary studies to explicitly account for the ecological networks that species are embedded in.
